Open Questions for Computer Science and Cheminformatics

### 2011-11-17 OpenQuestions.tex
Minot change

The key bonus of the semantic web is that different data sources can be readily integrated with each other. In the field
of Cheminformatics, we are not only interest in linking two molecules 
(this normalization problem for different protomers, tautomers, or special cases of isomerisms remains open), but we
are also interested in being able to search efficiently within molecules when being linked via semantic web approaches.
What could be algorithmic solutions for this?
\end{enumerate}

@@

\section*{Data mining}
evaluation of similarities in a heterogeneous network.  What is a specific example here?

integrate chemical structure information with ontologies.  Specific example problem?

Classify molecular descriptors up to equivalence, and dependence on one another.

systems-level understanding of small molecules.  What does this mean, and what would a specific challenge problem be?

>>>>

The key bonus of the semantic web is that different data sources can be readily integrated with each other. In the field
of Cheminformatics, we are not only interest in linking two molecules 
(the normalization problem for different protomers, tautomers, or special cases of isomerisms remains open), but we
are also interested in being able to search efficiently within molecules when being linked via semantic web approaches.
What could be algorithmic solutions for this?
\end{enumerate}

@@

\section*{Data mining}
\begin{itemize}
\item evaluation of similarities in a heterogeneous network.  What is a specific example here?
\item integrate chemical structure information with ontologies.  Specific example problem?
\item Classify molecular descriptors up to equivalence, and dependence on one another.
\item systems-level understanding of small molecules.  What does this mean, and what would a specific challenge problem be?
\end{itemize}
